### 2008-03-12 SAiP/Module1/H3/doc/softwarearchitecture.tex
Updating with contemplation for Bass definition

\fixme{Answer question 1.4}

>>>>

If the references to software and computing is removed the definition talks about elements, structures and properties, and their relations. This definition may be used about anything which may be broken down into generalised components. As an example could be used the construction of a rifle. Describing the elements that goes into making a rifle (hammer, barrol, ...), the structures that comes from putting them together, and the individual relationships that must be met (form fit, etc.). The elements may fit together in different ways and multiple structures may be required to complete the description. (the hammer up, the hammer down, etc.). The properties are in fact only the externally visible to the given element, as those are the only properties that are relevant to the architecture. These details include things like the strength of the metal, which may be different for the hammer and the pipe, the price range, produktion time, etc. while things like the cheak-pad may be optional.

The description of an architecture, as defined by Bass et. al. is therefore very general and apart from the use of words like "software" and "computer", may apply to any architecture, be it a building, a produktion line for a rifle, or a embedded software system.
